\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{tabularx}
\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*,itemsep=2pt,topsep=2pt}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

{\LARGE \textbf{Shashwat}}\\[3pt]
Bachelor of Engineering\\
Birla Institute of Technology and Science, Pilani\\
\href{tel:+917461012314}{+91-7461012314} $\vert$ 
\href{mailto:f20230266@pilani.bits-pilani.ac.in}{f20230266@pilani.bits-pilani.ac.in} $\vert$
\href{https://leetcode.com/shashwat-leetcode}{shashwat-leetcode}

\vspace{8pt}

\section*{Education}
\textbf{Birla Institute of Technology and Science, Pilani}, India \hfill Aug 2023 -- Jul 2027\\
Bachelor of Engineering in Civil\\
\textit{CGPA: [Placeholder: 0.00/10.00]}

\section*{Professional Experience}
\textbf{SWECHA Telangana} \hfill Remote\\
\textit{Software Engineer Intern} \hfill May 2024 -- Jul 2024
\begin{itemize}
    \item Architected a distributed GPU cluster by aggregating compute resources from multiple clients, achieving 100+ TFLOPS of combined throughput using the Petals distributed inference framework.
    \item Orchestrated cluster formation and secure node discovery through automated peer-to-peer networking protocols.
    \item Deployed a Telugu language model across the distributed cluster and executed fine-tuning workflows on domain-specific datasets.
    \item Fine-tuned TinyLlama-1.1B (4-bit quantized) using LoRA on 15K samples, improving task accuracy.
    \item Built and Dockerized a FastAPI-based LLM inference service with async request handling, token streaming, and request batching.
\end{itemize}

\section*{Projects}
\textbf{Distributed Cluster Manager} \hfill \textit{Resource Orchestration Application}
\begin{itemize}
    \item Developed an application that automates Exo installation and cluster connectivity using Tailscale for secure mesh networking.
    \item Implemented hardware-aware cluster matching to optimize node selection based on GPU specifications and network topology.
    \item Built a real-time resource monitoring dashboard with metrics for computational capacity (TFLOPS), node availability, and compute time allocation.
    \item Designed a heartbeat-based health monitoring system for automatic node failure detection and recovery.
    \item \textit{Tech Stack: [Placeholder: Python, FastAPI, Tailscale, Docker, React]}
\end{itemize}

\textbf{Log Monitoring Application} \hfill \textit{Full-Stack Monitoring System}
\begin{itemize}
    \item Built a backend (Spring Boot) and frontend (React) application to monitor append-only log files in real time.
    \item Used WatchService for efficient file monitoring and WebSockets for live client communication.
    \item Optimized the log reader to handle extremely large files (100+ GB) with minimal memory footprint.
    \item Implemented multi-client subscription support with play/pause controls via persistent WebSocket connections.
    \item Built a React frontend with scroll-lock and live log streaming to mimic terminal behavior.
    \item \textit{Project Link: [Placeholder: https://github.com/username/log-monitoring-app]}
\end{itemize}

\section*{Certifications and Courses}
\begin{itemize}
    \item Full Stack Web Development --- Comprehensive training in modern web technologies including React, Node.js, and database management.
    \item Data Structures and Algorithms --- Strong problem-solving foundation with 500+ problems solved on LeetCode.
    \item \textit{Additional Certifications: [Placeholder: AWS Cloud Practitioner, Kubernetes Fundamentals]}
\end{itemize}

\section*{Skills}
\textbf{Languages:} Python, Java, C/C++, JavaScript, SQL, HTML, CSS\\
\textbf{Databases:} MySQL, OracleDB, MongoDB\\
\textbf{Tools:} Docker, Kubernetes, Linux, Git, GitHub\\
\textbf{CS Fundamentals:} Data Structures \& Algorithms, Design Patterns, Object-Oriented Programming, DBMS\\
\textbf{Soft Skills:} Cross-team collaboration, stakeholder management, communication

\section*{Additional Information}
\textbf{LinkedIn:} [Placeholder: https://linkedin.com/in/your-profile]\\
\textbf{GitHub:} [Placeholder: https://github.com/your-username]\\
\textbf{Location:} [Placeholder: Pilani, Rajasthan, India]

\end{document}
